---
title: "BC Elections Statitics"
output:
  html_document:
    toc: yes
    toc_depth: 2
  pdf_document:
    toc: yes
    toc_depth: '2'
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r load libraries, message=FALSE}
library(infer)
library(palmerpenguins)
library(tidyverse)
library(rlang)
library(tidyverse)
```

## Part 1: Using bootstrapping on the data

```{r}
poll_data <- read_csv("data/angus_reid_poll.csv")

ci_pipeline <- function(sample) {
  sample %>%
    get_confidence_interval(level = 0.95, type = "percentile")
}

set.seed(2020)
boostrap_poll <- poll_data %>%
  rep_sample_n(size = nrow(.), replace = TRUE, reps = 10000) %>%
  count(party) %>%
  mutate(stat = n / 714) %>%
  select(-n) %>%
  group_by(party) %>%
  nest() %>%
  # boostrap dist for every party
#used data to calculate estimate, when I could have calculated directly from sample
  mutate(percentile_ci = map(data, ci_pipeline)) %>%
  mutate(point_estimate = map_dbl(data, ~ mean(.x$stat))) %>%
  unnest(percentile_ci)
print(boostrap_poll)

# reorder to go from biggest to smallest
ggplot(boostrap_poll, aes(x = reorder(party, -point_estimate), y = point_estimate, fill = party)) +
  geom_bar(stat = "identity") +
  geom_errorbar(aes(
    ymin = lower_ci,
    ymax = upper_ci), size = 1, width = 0.1) +
  xlab("BC Gov Parties") +
  ylab("Voting Proportions")

```

## Interepations of the boostrap plot
> I am 95% confident that the true mean votes (or true population proportion) of the NDP Party is between 0.451 and 0.525, with the point estimate being 0.488.

> I am 95% confident that the true mean votes (or true population proportion) of the Liberal Party is between 0.293 and 0.361, with the point estimate being 0.328.

> I am 95% confident that the true mean votes (or true population proportion) of the Green Party is between 0.112 and 0.162, with the point estimate being 0.137.

> I am 95% confident that the true mean votes (or true population proportion) of the Another Party is between 0.0322 and 0.0644, with the point estimate being 0.0476.

## Part 2: Using CLT on the data (single sample)

```{r}
set.seed(2020)
proportion_poll <- poll_data %>% 
group_by(party) %>%
summarize(successes = n(), stat = successes / nrow(poll_data)) %>%
mutate(StdError = sqrt(stat*(1-stat) / nrow(poll_data))) %>%
mutate(lower_95 = stat - (1.96 * StdError),
      upper_95 = stat + (1.96 * StdError))
proportion_poll

```

```{r}
proportion_poll %>% ggplot(aes(x=fct_reorder(party, stat, .desc = TRUE), y = stat, fill=party)) +
geom_bar(stat = "identity") +
geom_errorbar(data = proportion_poll, mapping = aes(ymin = lower_95, ymax = upper_95), width = 0.2) +
  xlab("BC Gov Parties") +
  ylab("Voting Proportions") + 
geom_label(aes(label=round(stat,3)))
```

## Final Summary and comparisons 


>Point estimate was 48.7% for NDP, 32.8% for Liberals, 13.7% for Green party, and 4.8% for the other parties. I am 95% confident that the CI is between 45% to 52.4% for NDP, 29.3% to 36.2% for Liberals, 11.2% to 16.2% for Green Party, and 3.2% to 6.3% for the other parties.

>There were no major differences from bootstrapping. This is because the sample fulfills the sample size criteria of the CLT, having enough successes/failures. In bootstrapping, many samples and calculated the PE and CIs, which should have been close to the true proportion. In Part 2, I just used one sample directly, and calculated simliar results. This is due to having a large enough sample size, allowing CLT to work.

```{r}

```
